# SK Overview

## Data and Packages

```{r data-and-packages}
library(tidyverse)
library(gt)
source(here::here("src/pipeline/transform.R"))
source(here::here("src/analysis/reporting.R"))

d0 <- load_data() 
d <- d0 |> clean_data()
```

## Sample

This analysis includes all Treatment and Non-RCT participants in Saskatchewan. 
The table below shows the number of participants in each SK cohort by assignment label. 

```{r sample}
dsk <- d |> filter(demo_province_fct == "Saskatchewan", assignment_label_fct != "Comparison")


t00 <- dsk |> 
  mutate(cohort_name = fct_reorder(cohort_name, date_of_enrollment)) |> 
  count(cohort_name, assignment_label_fct) |> 
  group_by(cohort_name) |> 
  mutate(Total = sum(n)) |> 
  ungroup() |> 
  tidyr::pivot_wider(names_from = assignment_label_fct, values_from = n)  |> 
  select(c(-Total), Total)

t00 |> 
  gt::gt() |> 
  gt::sub_missing(missing_text = "---") |> 
  gt::cols_align(align = "right", columns = 1) |> 
  gt::grand_summary_rows(
    columns = 2:4, 
    fns = list(Total = ~sum(.x, na.rm = TRUE))
  )

dl_button(t00, "t00-sample")
```

The total number of participants in our sample is `r nrow(filter(dsk, assignment_label_fct != "Control"))`.

## Baseline Characteristics

### Key Demographics
```{r hdesgs}
labs_lgl <- c(
  demo_immigrant_lgl = "Migration--Immigrant",
  demo_newcomer_lgl = "Migration--Newcomer (< 5 years in Canada)",
  demo_born_in_canada_lgl = "Migration--Born in Canada", 
  demo_receiving_ei_lgl = "Financial Assistance--Receiving EI",
  demo_receiving_ia_lgl = "Financial Assistance--Receiving Social Assistance", 
  demo_receiving_none_lgl = "Financial Assistance--None of the Above",
  demo_young_lgl = "Age--Youth (< 30)",
  demo_middle_age_lgl = "Age--Middle Age (30-64)",
  demo_old_lgl = "Age--Older (> 64)", 
  demo_racialized_lgl = "Marginalization Factors--Racialized", 
  demo_indigenous_lgl = "Marginalization Factors--Indigenous", 
  demo_bipoc_lgl = "Marginalization Factors--BIPOC",  
  demo_disability_lgl = "Marginalization Factors--Disability", 
  demo_woman_plus_lgl = "Marginalization Factors--Woman+",
  demo_mf_none_lgl = "Marginalization Factors--None of the Above"
)

t01 <- dsk |> 
  mutate(
    demo_born_in_canada_lgl = !demo_immigrant_lgl,
    demo_woman_plus_lgl = demo_gender_fct != "Man" | demo_transgender_lgl, 
    demo_receiving_none_lgl = demo_receiving_ei_lgl + demo_receiving_ia_lgl == 0, 
    demo_young_lgl = demo_age < 30, 
    demo_old_lgl = demo_age > 64,
    demo_middle_age_lgl = demo_young_lgl + demo_old_lgl == 0, 
  ) |> 
  select(enrollment_id, matches('^demo_.*lgl$'))  |> 
  rowwise() |> 
  mutate(
    demo_mf_none_lgl = sum(
      c_across(
        matches("^demo_(racialized|indigenous|bipoc|disability|woman_plus)_lgl")
      )
    ) == 0
  ) |> 
  ungroup() |> 
  select(-matches("trans|in_sk|parent")) |> 
  pivot_longer(cols = c(-enrollment_id), names_to = "var", values_to = "val", cols_vary = "slowest") |>
  mutate(var = fct_inorder(var)) |>  
  filter(!is.na(val)) |> 
  group_by(var) |> 
  summarize(N = n(), n = sum(val), p = n / N)  |> 
  mutate(lab = labs_lgl[as.character(var)]) |>
  separate(lab, into = c("cat", "var"), sep = "--", extra = "merge") |> 
  select(cat, var, N, n, p)

t01 |> 
  group_by(cat) |> 
  gt(rowname_col = "var") |>
  tab_stub_indent(rows = everything()) |> 
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups(groups = everything())
  ) |> 
  fmt_percent(columns = p, decimals = 0) |> 
  cols_align(align = "right", columns = 1) |> 
  gtExtras::gt_plt_bar(column = p, keep_column = TRUE, color = "lightblue")

dl_button(t01, "t01-demographics")
```


### Education 
```{r baseline-education}
t02 <- dsk |>
  filter(!is.na(educ_max_fct)) |> 
  group_by(educ_max_fct) |> 
  summarize( 
    n = n(), 
    .groups = 'drop'
  ) |> 
  mutate(
    N = sum(n),
    p = n / N
  ) |> 
  select(`Baseline Highest Education` = educ_max_fct, N, n, p) 

t02 |> 
  gt::gt() |> 
  gt::fmt_percent(columns = p, decimals = 0) |> 
  gt::cols_align(align = "right", columns = 1) |> 
  gtExtras::gt_plt_bar(column = p, keep_column = TRUE, color = "lightblue")

dl_button(t02, "t02-education")
```

## Program Satisfaction

```{r program-satisfaction}
t03 <- dsk |> 
  select(enrollment_id, matches("^satis")) |> 
  pivot_longer(cols = -enrollment_id, names_to = "var", values_to = "val") |> 
  mutate(var = fct_inorder(var)) |> 
  filter(!is.na(val)) |> 
  group_by(var) |> 
  summarize(N = n(), n = sum(val), p = n / N) |> 
  select(lab = var, N, n, p)

t03 |> 
  gt::gt() |> 
  gt::fmt_percent(columns = p, decimals = 0) |> 
  gt::cols_align(align = "right", columns = 1) |> 
  gtExtras::gt_plt_bar(column = p, keep_column = TRUE, color = "lightblue")

dl_button(t03, "t03-satisfaction")
```

## Outcomes

### Employment Hope

```{r employment-hope}
t04 <- dsk |>
  select(enrollment_id, ehs) |> 
  unnest(ehs) |> 
  pivot_longer(
    cols = matches("^ehs_"), 
    names_to = "var", 
    values_to = "val", 
    cols_vary = "slowest"
  ) |> 
  mutate(var = fct_inorder(var), survey_tag = fct_reorder(survey_tag, survey_time)) |> 
  filter(!is.na(val)) |>
  group_by(var, survey_tag) |> 
  summarize(
    N = n(), 
    mean = mean(val), 
    sd = sd(val), 
    .groups = 'drop'
  ) |> 
  group_by(var)


t04 |> 
  gt::gt() |> 
  gt::cols_align(align = "right", columns = 1) |> 
  gtExtras::gt_plt_bar(column = mean, keep_column = TRUE, color = "lightblue") |> 
  gt::fmt_number(columns = c(mean, sd), decimals = 1)

dl_button(t04, "t04-ehs-14")

```

### Employment Status
```{r outcomes}
d_out <- dsk |> 
  select(enrollment_id, outcomes) |> 
  unnest(outcomes) |> 
  arrange(desc(survey_version), survey_time) |> 
  mutate(survey_tag = fct_inorder(survey_tag) |> fct_relevel("12-month-follow-up", after = Inf))

t05 <- d_out |> 
  group_by(survey_tag) |>
  filter(!is.na(job_employed)) |> 
  summarize(
    N = n(), 
    Employed = mean(job_employed), 
    Enrolled = mean(educ_enrolled, na.rm = TRUE), 
    NEET = 1 - Employed - Enrolled,
  ) 

t05 |> 
  gt::gt() |> 
  gt::cols_align(align = "right", columns = 1) |> 
  gt::fmt_percent(columns = c(Employed, Enrolled, NEET), decimals = 0)

dl_button(t05, "t05-employment-status")
```

### Compensation (Among Employed)

```{r compensation}
t06 <- d_out |> 
  filter(job_employed %in% TRUE) |> 
  group_by(survey_tag) |> 
  summarize(
    N = n(), 
    across(matches("^job_benefits|^job_annualized_salary"), function(x) mean(x, na.rm = TRUE))
  ) |> 
  select(survey_tag, N, job_annualized_salary,  matches("^job_benefits")) |> 
  rename_all(~str_replace(., "job_benefits|job_", "")) |> 
  select(-c(`_none`, `_n`, `_any`), `_any`, `_total` = `_n`)

t06 |> 
  gt::gt() |> 
  gt::cols_align(align = "right", columns = 1) |> 
  gt::fmt_percent(columns = c(matches("^_[^t]")), decimals = 0) |> 
  gt::fmt_number(columns = c(`_total`), decimals = 1) |> 
  gt::fmt_currency(columns = c(annualized_salary), currency = "CAD", decimals = 0) |> 
  gt::tab_spanner(columns = c(matches("^_")), label = "Benefits")

dl_button(t06, "t06-compensation")
```